The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

###Neccesary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social deiscout rate, but will also need to consider the potential GDP increase brought about by improved education policies.

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but the study considers how this increased self-confidence positively affects GDP and the rate of entrepeurship in a given country. It will therefore need to include some quantiative approach to measuring this factor.

@@

4. Types of management: This study focuses on social issues and how these factors affect entrepreneurship, but management styles can transcend social norms. Control variables will need to be identified to address this.

>>>>

###Neccesary Concepts  
1. Return on Investment: Assigning a future Euro value to a present-day investment. This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.

2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.

@@
